### 2021-04-01 papers/SYRCoSE/regmachine-eventstruct.tex
SYRCoSE: WIP --- reworking text

>>>>

Finally, we need a way to reconcile the event structure
with the states of machine's threads. 
To do so we use a function $\thrdmap : \eventSet \fun \ThrdState$
which maps event to a thread state obtained as a result of
execution of event's side-effect.

Let us consider an example. 
\todo{}

The rules of operational semantics constructing 
the event structure are presented on~\cref{fig:eventstruct-sem}.

\input{fig/eventstruct-sem.tex}
